Astr 513: Final Project

### 2016-04-28 Final_Project/ms.tex
Began writing document
I began writing on the data. I also added a bibliography file that we
can edit and the apj.bst for the bibliography style I put in the tex
document, although if you guys would prefer a different style, we can
change that.

\documentclass[12pt,a4paper]{article}
\usepackage{amsmath}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage{enumerate}
\usepackage[makeroom]{cancel}
\usepackage{hyperref}

@@

@@

\section*{References}

\begin{enumerate}
  \item test
\end{enumerate}

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage{amsmath}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage{enumerate}
\usepackage[makeroom]{cancel}
\usepackage{hyperref}
\usepackage{natbib}
\bibliographystyle{apj}

@@

% Roman numerals command
\makeatletter
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

% Some definitions for writing SN, SNe, SN Ia, and SNe Ia...
\newcommand{\sn}{\mbox{SN}}
\newcommand{\sne}{\mbox{SNe}}
\newcommand{\sna}{\mbox{SN \rom{1}a}}
\newcommand{\snea}{\mbox{SNe \rom{1}a}}

@@

\section{Data}
\label{sec:data}

Our data is compiled from \citet{betoule2014} and \citet{rest2014} blah blah blah...

\subsection{The JLA sample}
\label{sec:betoule}

\citet{betoule2014} define their ``joint light-curve analysis'' (JLA) sample, a total of 740 type Ia supernovae (SNe Ia) %If we define the abbreviations elsewhere, this can change -- ELW
 compiled from a combination of data from the Sloan Digital Sky Survey (SDSS), the Supernova Legacy Survey (SNLS), the Hubble Space Telescope (HST), and several other experiments. The 613 SDSS \snea{} come from the SDSS supernova survey (SDSS-SNS) of SDSS-II \citep{sako2014} with redshifts of $0.05 < z < 0.4$, and 374 of them are selected from those that were confirmed in the spectroscopic follow-up. The rest of the \sne{} come from the compilation by \citet{conley2011}, which includes 242 spectroscopically confirmed \snea{} from SNLS at redshifts $0.2 < z < 1$, 14 \snea{} from HST at very high redshifts of $0.7 < z < 1.4$, and 123 low redshift ($z < 0.08$) from a variety of sources. We made use of the publicly available distance moduli, redshifts, and covariance matrix provided by \citet{betoule2014}\footnote{Data is available for download via \url{http://cdsweb.u-strasbrg.fr/cgi-bin/qcat?J/A+A/568/A22}}. We note that the distance moduli are binned, so that they are only computed and given on a grid of redshifts. The distance modulus can then be well approximated by a piecewise linear function of $\log(z)$ that is given in a single redshift bin $z_b \le z < z_{b+1}$ as \citep[see][Appendix E.1]{betoule2014}
\begin{equation}
\label{eq:binnedMu}
\bar{\mu}(z) = (1 - \alpha) \mu_b + \alpha \mu_{b+1},
\end{equation}
where they have defined $\alpha = \log\left(\frac{z}{z_b}\right)/\log\left(\frac{z_{b+1}}{z_b}\right)$ and $\mu_i$ is the distance modulus at control point $z_i$. Therefore, the data and covariance matrix are merely given at the 31 control points log-spaced in the redshift range $0.01 < z < 1.3$.

%\section*{References}
%
%\begin{enumerate}
%  \item test
%\end{enumerate}

\bibliography{final}
